\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{geometry}
\usepackage{longtable}
\usepackage{array}
\usepackage{fancyhdr}
\usepackage{lmodern}

\geometry{margin=2.5cm}

\setlength{\parskip}{0.5em}
\setlength{\parindent}{0pt}

% ── Table of contents depth ──────────────────────────────────
\setcounter{tocdepth}{2}

% ── Verbatim-like command for file/package names ─────────────
\newcommand{\pkg}[1]{\texttt{\textbf{#1}}}
\newcommand{\file}[1]{\texttt{#1}}
\newcommand{\topic}[1]{\texttt{\small #1}}

% ── Purpose box: indented italic block ───────────────────────
\newenvironment{filebox}{%
  \par\vspace{0.3em}\begin{quote}\itshape
}{%
  \end{quote}\vspace{0.3em}%
}

% ── Fancyhdr ─────────────────────────────────────────────────
\pagestyle{fancy}
\fancyhf{}
\rhead{\small UR3e Workspace --- Source Documentation}
\lhead{\small \texttt{ur3e\_ws/src}}
\cfoot{\thepage}

% ─────────────────────────────────────────────────────────────
\begin{document}

% ── Title page ───────────────────────────────────────────────
\begin{titlepage}
  \centering
  \vspace*{3cm}
  {\Huge\bfseries UR3e Workspace}\par
  \vspace{0.5em}
  {\Large Source Package Documentation}\par
  \vspace{2em}
  {\large\texttt{ur3e\_ws/src/}}\par
  \vspace{3em}
  \noindent\rule{\linewidth}{0.6pt}\par
  \vspace{0.5em}
  \begin{minipage}{0.85\linewidth}
    \centering
    This document describes every file and package inside the
    \texttt{src/} directory of the UR3e ROS\,2 workspace.
    The workspace implements a complete pick-and-place pipeline:
    \textbf{UR3e arm} $+$ \textbf{RealSense D435 camera} $+$
    \textbf{YOLO shoe detection} $+$ \textbf{MoveIt\,2 motion planning},
    with support for two gripper configurations
    (Robotiq\,2F-85 and OnRobot\,2FG7).
  \end{minipage}\par
  \vspace{0.5em}
  \noindent\rule{\linewidth}{0.6pt}\par
  \vfill
  {\small May 2026}
\end{titlepage}

\tableofcontents
\newpage

% ═══════════════════════════════════════════════════════════════
\section{Project Overview}
% ═══════════════════════════════════════════════════════════════

The workspace targets the \textbf{Universal Robots UR3e} collaborative arm
equipped with a \textbf{Intel RealSense D435} RGB-D camera mounted on the
end-effector. The main goal is to autonomously pick shoes from an unstructured
workspace by detecting the shoe's lacing hole with a YOLO segmentation model,
computing a 3-D grasp point in robot-frame coordinates, and executing a
pick-and-place motion with MoveIt\,2.

\subsection*{Data flow}

\begin{enumerate}
  \item The \textbf{RealSense camera node} publishes colour and depth frames.
  \item The \textbf{GraspDetector} (\file{shoe\_detector}) runs YOLO on each
        frame, extracts the ``hole'' segmentation mask, computes the grasp
        centre via PCA, back-projects to 3-D with the RealSense depth,
        transforms to \texttt{base\_link} and publishes
        \topic{/shoe\_detector/grasp\_point\_base}.
  \item \textbf{pick\_and\_place\_grasp.py} subscribes to that topic,
        collects a median of several samples to filter noise, then commands
        the UR3e through a full pick-and-place sequence via MoveIt\,2.
  \item The \textbf{hand-eye calibration} (done once with \pkg{easy\_handeye2})
        supplies the static TF between \texttt{tool0} and
        \texttt{camera\_color\_optical\_frame}, enabling the
        depth-to-robot-frame transform at step~2.
\end{enumerate}

\subsection*{Package map}

\begin{center}
\begin{tabular}{|l|l|}
\hline
\textbf{Category} & \textbf{Packages} \\
\hline
Custom (your code) &
  \pkg{ur\_sim}, \pkg{shoe\_detector}, \pkg{ur\_moveit}, \pkg{ur\_gripper\_moveit} \\
Robot driver &
  \pkg{Universal\_Robots\_ROS2\_Driver} (7 sub-packages) \\
Robot description &
  \pkg{Universal\_Robots\_ROS2\_Description} \\
Simulation &
  \pkg{Universal\_Robots\_ROS2\_GZ\_Simulation}, \pkg{gz\_ros2\_control} \\
Control framework &
  \pkg{ros2\_control} (10 sub-packages) \\
Perception &
  \pkg{aruco\_ros} (aruco + aruco\_msgs + aruco\_ros) \\
Calibration &
  \pkg{easy\_handeye2} (easy\_handeye2 + easy\_handeye2\_msgs) \\
Gripper (Robotiq) &
  \pkg{ros2\_robotiq\_gripper} \\
Gripper (OnRobot) &
  \pkg{onrobot\_2FG7\_gripper\_description} \\
Motion planning API &
  \pkg{pymoveit2} \\
Gazebo assets &
  \pkg{models} \\
\hline
\end{tabular}
\end{center}

\newpage
% ═══════════════════════════════════════════════════════════════
\section{Custom Packages}
% ═══════════════════════════════════════════════════════════════

These are the packages written specifically for this project.
They contain all the application logic.

% ───────────────────────────────────────────────────────────────
\subsection{\texttt{shoe\_detector} --- YOLO perception and grasp estimation}
% ───────────────────────────────────────────────────────────────

A ROS\,2 Python package that bridges the YOLO object-detection library
(Ultralytics) with the ROS\,2 graph. It provides two independent nodes and
one launch file.

\subsubsection{\file{shoe\_detector/yolo\_node.py}}

\begin{filebox}
\textbf{Purpose:} Bare-bones object detection publisher. Runs YOLO on every
incoming colour frame and republishes two things: a visually annotated image
and a structured \texttt{Detection2DArray} message containing bounding boxes,
class IDs, and confidence scores for all detected objects.
\end{filebox}

\begin{itemize}
  \item Subscribes to \topic{/camera/camera/color/image\_raw}.
  \item Loads the \file{.pt} model from a hard-coded path at startup.
  \item Publishes annotated frames on \topic{/shoe\_detector/image\_annotated}.
  \item Publishes detections on \topic{/shoe\_detector/detections}
        (\texttt{vision\_msgs/Detection2DArray}).
  \item Does \emph{not} use depth; it is a pure 2-D detector.
  \item \textbf{Note:} the model path is hard-coded. Use
        \file{grasp\_detector.py} for production, which accepts the path as
        a ROS\,2 parameter.
\end{itemize}

\subsubsection{\file{shoe\_detector/grasp\_detector.py}}

\begin{filebox}
\textbf{Purpose:} Full perception pipeline. Detects the shoe lacing hole,
computes a 6-DOF grasp point in the robot base frame, and publishes it so
that the motion planning script can pick up and execute without any manual
coordinate entry.
\end{filebox}

\textbf{Algorithm:}
\begin{enumerate}
  \item Time-synchronises the colour and aligned depth streams from the
        RealSense using \texttt{message\_filters.ApproximateTimeSynchronizer}.
  \item Runs YOLO segmentation inference; selects the highest-confidence
        detection of class \texttt{target\_class} (default: \texttt{hole}).
  \item Applies PCA to the binary segmentation mask to find the principal
        and minor axes of the hole shape.
  \item Marches along the \emph{minor} axis from the centre outward to find
        the two rim contact points for the gripper fingers.
  \item Reads the RealSense depth at the centre and both rim pixels, with
        three fallback strategies when the hole interior returns no valid
        depth (IR can fail on dark or transparent surfaces).
  \item Back-projects all three pixels to 3-D camera-frame coordinates using
        the pinhole model and the live \texttt{CameraInfo} intrinsics.
  \item Transforms to \texttt{base\_link} via TF\,2 (requires the hand-eye
        static TF to be running).
  \item Publishes three \texttt{PointStamped} topics and a debug image:
        \topic{/shoe\_detector/grasp\_point\_base} (centre),
        \topic{/shoe\_detector/grasp\_left\_base},
        \topic{/shoe\_detector/grasp\_right\_base}.
\end{enumerate}

\textbf{Configurable parameters (passed with \texttt{-{}-ros-args -p}):}

\begin{center}
\begin{tabular}{|l|l|p{6cm}|}
\hline
\textbf{Parameter} & \textbf{Default} & \textbf{Meaning} \\
\hline
\texttt{model\_path} & (required) & Path to the \texttt{.pt} YOLO weights \\
\texttt{target\_class} & \texttt{hole} & YOLO class name to target \\
\texttt{conf\_threshold} & \texttt{0.5} & Minimum detection confidence \\
\texttt{color\_topic} & \texttt{/camera/.../color/image\_raw} & RGB input \\
\texttt{depth\_topic} & \texttt{/camera/.../aligned\_depth...} & Depth input \\
\texttt{show\_window} & \texttt{true} & Show OpenCV preview window \\
\hline
\end{tabular}
\end{center}

\subsubsection{\file{shoe\_detector/\_\_init\_\_.py}}

Empty marker file that makes \texttt{shoe\_detector/} a Python package,
required by the \texttt{ament\_python} build system.

\subsubsection{\file{models/best\_kaagle\_10mars.pt}}

The trained YOLO segmentation weights ($\approx$5\,MB). Trained on a custom
dataset containing shoe images with ``hole'' (lacing hole) and ``shoe'' class
labels. The filename encodes the training date (10 March) and dataset origin
(Kaggle).

\subsubsection{\file{config/handeye.yaml}}

Stores the hand-eye calibration result in the format produced by
\pkg{easy\_handeye2}: the rigid transform from \texttt{tool0} to
\texttt{camera\_color\_optical\_frame} as a translation + quaternion.
Read at startup by \file{perception.launch.py} to publish the static TF.

\subsubsection{\file{launch/perception.launch.py}}

\begin{filebox}
\textbf{Purpose:} One-shot launch file for the entire perception stack on the
real robot. Starts the RealSense camera and publishes the hand-eye TF.
\end{filebox}

Launches two things:
\begin{itemize}
  \item \textbf{RealSense\,2 camera} via \file{rs\_launch.py}, configured for
        $640\times480$ @ 30\,fps, with depth-to-colour alignment and point cloud
        enabled. Camera TF publication is disabled (\texttt{publish\_tf:=false})
        because the hand-eye transform supplies the camera pose instead.
  \item \textbf{Static TF publisher} (\texttt{tf2\_ros}) that broadcasts the
        hard-coded hand-eye calibration result (translation + quaternion),
        placing \texttt{camera\_color\_optical\_frame} relative to \texttt{tool0}.
\end{itemize}

\subsubsection{\file{setup.py} and \file{setup.cfg}}

Standard \texttt{ament\_python} build files. \file{setup.py} declares the
package name, entry points for the two nodes (\texttt{yolo\_node} and
\texttt{grasp\_detector}), and lists the data files (model weights, config,
launch files) to install.

\subsubsection{\file{setup.py.save}}

Leftover backup of \file{setup.py} created by a text editor.
Not used; safe to delete.

\subsubsection{\file{shoe\_detector/\_\_pycache\_\_/}}

Python bytecode cache. Automatically regenerated; safe to delete.

\subsubsection{\file{test/test\_copyright.py}, \file{test\_flake8.py}, \file{test\_pep257.py}}

Auto-generated linting tests created by the \texttt{ament\_python} package
template. They check licence headers, PEP\,8 compliance, and docstring
formatting. They do not test application logic.

% ───────────────────────────────────────────────────────────────
\subsection{\texttt{ur\_sim} --- Simulation launch files and motion scripts}
% ───────────────────────────────────────────────────────────────

The central custom package. Contains all URDF/Xacro robot descriptions for
the simulation, Gazebo world files, controller configurations, and every
Python motion script.

\subsubsection{URDF / Xacro files (\file{urdf/})}

\begin{description}
  \item[\file{ur3e.urdf.xacro}]
    Top-level robot description for the bare UR3e (no gripper). Includes
    the UR3e kinematics macro and the ROS\,2 control interface. Used by
    \file{spawn\_ur3e.launch.py}.

  \item[\file{ur3e\_macro.xacro}]
    Kinematics macro for the UR3e body: link geometry, inertia, collision
    meshes, and joint limits. Parametrised so it can be composed with
    different end-effectors.

  \item[\file{ur3e.ros2\_control.xacro}]
    Declares the \texttt{ros2\_control} hardware interface for the bare arm.
    Switches between the real Gazebo Ignition hardware plugin
    (\texttt{ign\_ros2\_control/IgnitionSystem}) and the mock hardware
    interface depending on the \texttt{sim\_ignition} argument.

  \item[\file{ur3e\_gripper.urdf.xacro}]
    Top-level description for the UR3e with the \textbf{OnRobot 2FG7} gripper
    attached. Composes the arm macro with the OnRobot xacro and a combined
    \texttt{ros2\_control} block covering both the arm and the gripper.
    Used by \file{spawn\_ur3e\_gripper.launch.py}.

  \item[\file{robotiq\_2f\_85\_gripper.urdf.xacro}]
    Standalone top-level description for the \textbf{Robotiq 2F-85} gripper,
    assembled from the macro below.

  \item[\file{robotiq\_2f\_85\_macro.urdf.xacro}]
    Parametric macro defining the Robotiq 2F-85 link/joint geometry.
    Imported by the gripper description and by other compositions.

  \item[\file{2f\_85.ros2\_control.xacro}]
    ROS\,2 control hardware interface block for the Robotiq 2F-85 gripper,
    wiring it to the \texttt{robotiq\_2f\_85\_gripper\_hardware} plugin.
\end{description}

\subsubsection{Gazebo world files (\file{worlds/})}

\begin{description}
  \item[\file{ur3e\_on\_table.sdf}]
    The main simulation world: a table surface, ambient lighting, and gravity.
    Spawns the robot on top of the table at the same height as the real setup.

  \item[\file{cubes.sdf}]
    World containing several coloured cubes for basic pick-and-place testing
    (no shoe geometry).

  \item[\file{cubes1.sdf}]
    Variant of \file{cubes.sdf} with a slightly different cube arrangement.
\end{description}

\subsubsection{Controller configuration (\file{config/})}

\begin{description}
  \item[\file{ur3e\_controllers.yaml}]
    Controller manager configuration for the arm only: activates
    \texttt{joint\_trajectory\_controller} (the arm trajectory controller used
    by MoveIt\,2) and \texttt{joint\_state\_broadcaster}.

  \item[\file{ur3e\_gripper\_controllers.yaml}]
    Same as above but includes an additional controller entry for the gripper.

  \item[\file{initial\_positions.yaml}]
    Defines the joint angles at which the robot spawns in Gazebo
    (typically a safe upright posture).
\end{description}

\subsubsection{Launch files (\file{launch/})}

\begin{description}
  \item[\file{spawn\_ur3e.launch.py}]
    Launches Gazebo with \file{ur3e\_on\_table.sdf}, spawns the bare UR3e,
    starts \texttt{robot\_state\_publisher}, and activates the arm controllers.

  \item[\file{spawn\_ur3e\_moveit.launch.py}]
    Extends \file{spawn\_ur3e.launch.py} by also starting the MoveIt\,2
    \texttt{move\_group} node using the \pkg{ur\_moveit} configuration.
    This is the primary launch file for simulation-based pick-and-place.

  \item[\file{spawn\_ur3e\_gripper.launch.py}]
    Same as \file{spawn\_ur3e.launch.py} but spawns \file{ur3e\_gripper.urdf.xacro}
    (UR3e + OnRobot 2FG7) and loads the gripper controllers.

  \item[\file{spawn\_ur3e\_gripper\_moveit.launch.py}]
    Extends the gripper spawn with MoveIt\,2, using the
    \pkg{ur\_gripper\_moveit} configuration.

  \item[\file{view\_ur3e.launch.py}]
    Publishes the robot URDF and opens RViz for visual inspection of the bare
    UR3e without Gazebo. Useful for checking URDF validity.

  \item[\file{view\_ur3e\_gripper.launch.py}]
    Same as above for the UR3e + OnRobot 2FG7 assembly.
\end{description}

\subsubsection{RViz configuration (\file{rviz/})}

\begin{description}
  \item[\file{view\_ur3e.rviz}]
    Pre-configured RViz layout showing the robot model and TF tree.
    Loaded by the \texttt{view\_*} launch files.
\end{description}

\subsubsection{Motion scripts (\file{scripts/})}

All scripts communicate with MoveIt\,2 via \pkg{pymoveit2}. They target the
\textbf{real robot} unless otherwise noted.

\begin{description}

  \item[\file{pick\_and\_place\_grasp.py}]
    \textbf{(production script.)}
    Full autonomous pick-and-place driven by the \pkg{shoe\_detector}
    grasp estimation. Subscribes to \topic{/shoe\_detector/grasp\_point\_base},
    collects a configurable number of samples and takes their spatial median
    to filter detector noise, validates that the pose is inside the UR3e
    workspace bounds, then executes a 9-step sequence:
    home $\to$ approach $\to$ descend $\to$ close gripper $\to$ retreat
    $\to$ safe transit $\to$ above drop $\to$ descend to drop $\to$
    open gripper $\to$ home.
    Includes a collision scene (table slab + camera-mount box) so MoveIt\,2
    avoids collisions. Ignores the camera Z coordinate (too noisy for depth
    sensing over the hole) and uses a fixed \texttt{PICK\_Z} instead.
    Implements retry logic with up to 3 planning attempts per step and a
    clean abort-to-home on failure.

  \item[\file{pick\_and\_place.py}]
    Earlier version of the pick-and-place with fixed (hard-coded) pick
    coordinates. Does not subscribe to the shoe detector. Documents three
    key bug-fixes discovered during development: wrong MoveIt\,2 group name,
    table-collision false positives, and joint-angle wrap-around causing
    \texttt{PATH\_TOLERANCE\_VIOLATED} errors.

  \item[\file{stack.py}]
    Simulation script for moving to a target Cartesian pose and picking up
    a cube in Gazebo. Uses a TF\,2-based arrival check: reads the actual
    \texttt{tool0} position from Gazebo and compares it to the commanded pose
    rather than trusting MoveIt\,2's reported execution result. Requires
    \texttt{use\_sim\_time:=true}.

  \item[\file{tp\_ar.py}]
    Joint-angle validation script for a kinematics lab exercise. Moves the
    arm to a set of joint angles (specified in degrees in the script), then
    reads back the real \texttt{tool0} position via TF\,2 and prints it so
    the result can be compared with an Octave forward-kinematics calculation.

  \item[\file{grasp\_test.py}]
    Pick-and-place driven by the grasp detector --- an intermediate version
    of \file{pick\_and\_place\_grasp.py} from before the median-filter and
    workspace-validation logic was added. Superseded.

  \item[\file{pick\_place\_test.py}]
    Intermediate step between \file{pick\_and\_place.py} (fixed coords) and
    \file{pick\_and\_place\_grasp.py} (detector-driven). Tests the full
    9-step sequence with semi-fixed coordinates.

  \item[\file{pick\_test.py}]
    Minimal script that only executes the pick half (home $\to$ approach
    $\to$ descend $\to$ close gripper), used to verify pick motion in
    isolation.

  \item[\file{stack\_old.py}]
    Earlier iteration of \file{stack.py} without the TF\,2 arrival
    verification. Superseded.

  \item[\file{stack (copy).py}]
    Unnamed copy of \file{stack.py} from a mid-development stage.
    Identical in content; safe to delete.

  \item[\file{stack\_bu\_new.py}]
    Another intermediate version of the stacking script (\textit{bu} = backup).
    Safe to delete.

  \item[\file{sb.py} and \file{sb2.py}]
    Sandbox scripts used during early development to test individual
    \pkg{pymoveit2} API calls (move to pose, move to joints,
    \texttt{wait\_until\_executed}).
    Safe to delete.

  \item[\file{test.py} and \file{test\_move.py}]
    Minimal test programs for single-arm movements written at the start of
    development. Not part of any pipeline. Safe to delete.

\end{description}

\subsubsection{\file{package.xml} and \file{CMakeLists.txt}}

Standard ROS\,2 package manifest and CMake file. \file{package.xml} declares
dependencies on \texttt{pymoveit2}, \texttt{moveit\_ros\_planning\_interface},
\texttt{ur\_description}, \texttt{ros\_gz\_sim}, and the gripper packages.
\file{CMakeLists.txt} installs launch files, config, scripts, and URDF assets.

% ───────────────────────────────────────────────────────────────
\subsection{\texttt{ur\_moveit} --- MoveIt\,2 configuration (arm only)}
% ───────────────────────────────────────────────────────────────

A MoveIt\,2 Setup-Assistant-generated package that configures motion
planning for the \textbf{bare UR3e} (no gripper). Used by
\file{spawn\_ur3e\_moveit.launch.py}.

\subsubsection{Config files (\file{config/})}

\begin{description}
  \item[\file{ur.urdf.xacro}]
    Entry-point URDF for MoveIt\,2. Parametrised to work with both the real
    driver and the Gazebo Ignition hardware interface via the
    \texttt{sim\_ignition} argument.

  \item[\file{ur.srdf}]
    Semantic Robot Description Format. Defines the planning group
    \texttt{ur\_manipulator} (all six arm joints), the home position, and
    lists self-collision pairs that can be safely ignored.

  \item[\file{ur.ros2\_control.xacro}]
    Hardware interface declaration consumed by the MoveIt\,2 configuration
    builder to wire controllers to planning groups.

  \item[\file{kinematics.yaml}]
    Specifies the IK solver plugin and parameters.
    Uses \texttt{kdl\_kinematics\_plugin/KDLKinematicsPlugin} for the
    \texttt{ur\_manipulator} group.

  \item[\file{ompl\_planning.yaml}]
    OMPL planner configurations: planner list, goal tolerances, planning
    time limits, and per-planner parameters such as range and goal bias.

  \item[\file{moveit\_controllers.yaml}]
    Maps MoveIt\,2 controller handles to the underlying
    \texttt{ros2\_control} controllers (the \texttt{joint\_trajectory\_controller}).

  \item[\file{ros2\_controllers.yaml}]
    Controller manager configuration used when MoveIt\,2 spawns its own
    controller manager (demo mode, without an external driver).

  \item[\file{joint\_limits.yaml}]
    Per-joint velocity and acceleration limits applied by MoveIt\,2 during
    trajectory scaling.

  \item[\file{initial\_positions.yaml}]
    Starting joint angles for the MoveIt\,2 fake controller (demo mode).

  \item[\file{chomp\_planning.yaml}, \file{lerp\_planning.yaml}, \file{trajopt\_planning.yaml}, \file{pilz\_industrial\_motion\_planner\_planning.yaml}, \file{pilz\_cartesian\_limits.yaml}]
    Configuration for alternative planners (CHOMP, LERP, TrajOpt, Pilz)
    generated by the Setup Assistant.

  \item[\file{moveit.rviz}]
    RViz configuration with the MoveIt\,2 Motion Planning panel pre-loaded.
\end{description}

\subsubsection{Launch files (\file{launch/})}

\begin{description}
  \item[\file{demo.launch.py}]
    All-in-one demo launcher: starts \texttt{robot\_state\_publisher},
    \texttt{move\_group}, RViz, and a fake joint-state publisher.
    Does not require Gazebo or a real robot; useful for testing the SRDF and
    planner configuration.

  \item[\file{move\_group.launch.py}]
    Starts only the \texttt{move\_group} node. Intended to be included by
    other launch files such as \file{spawn\_ur3e\_moveit.launch.py}.

  \item[\file{moveit\_rviz.launch.py}]
    Opens RViz pre-configured with the MoveIt\,2 Motion Planning panel.

  \item[\file{rsp.launch.py}]
    Starts the \texttt{robot\_state\_publisher} with the URDF from this
    package (RSP = Robot State Publisher).

  \item[\file{spawn\_controllers.launch.py}]
    Spawns and activates the ROS\,2 controllers listed in
    \file{ros2\_controllers.yaml} via the controller manager service.

  \item[\file{static\_virtual\_joint\_tfs.launch.py}]
    Publishes static TF transforms for virtual joints defined in the SRDF
    (e.g.\ world $\to$ base\_link).

  \item[\file{setup\_assistant.launch.py}]
    Re-opens the MoveIt\,2 Setup Assistant pre-loaded with this package,
    for iterative configuration editing.

  \item[\file{warehouse\_db.launch.py}]
    Starts the MongoDB warehouse used to persist MoveIt\,2 scenes and motion
    plans across sessions.
\end{description}

\subsubsection{\file{.setup\_assistant}}

Binary metadata file written by the MoveIt\,2 Setup Assistant.
Not edited manually.

% ───────────────────────────────────────────────────────────────
\subsection{\texttt{ur\_gripper\_moveit} --- MoveIt\,2 configuration (arm + OnRobot 2FG7)}
% ───────────────────────────────────────────────────────────────

Identical in structure to \pkg{ur\_moveit} but generated for the
\textbf{UR3e + OnRobot 2FG7 gripper} assembly. The SRDF defines two planning
groups: \texttt{ur\_manipulator} (the six arm joints) and \texttt{gripper}
(the 2FG7 finger joints). Loaded by
\file{spawn\_ur3e\_gripper\_moveit.launch.py}.

All files (\file{config/*.yaml}, \file{config/ur.srdf}, \file{launch/*.py})
serve the same roles as their equivalents in \pkg{ur\_moveit}; refer to
that section for descriptions. The key differences are:
\begin{itemize}
  \item \file{ur.urdf.xacro} includes the OnRobot 2FG7 xacro.
  \item \file{ur.srdf} adds the \texttt{gripper} planning group and new
        collision-exclusion pairs for the gripper links.
  \item \file{moveit\_controllers.yaml} maps a second controller handle for
        the gripper.
\end{itemize}

% ───────────────────────────────────────────────────────────────
\subsection{\texttt{models/class\_table} --- Gazebo world model}
% ───────────────────────────────────────────────────────────────

An SDFormat model of a table used in the Gazebo world files.

\begin{description}
  \item[\file{model.config}]
    Model metadata (name, version, description) read by the Gazebo model
    database.
  \item[\file{model.sdf}]
    Geometry and physics: a flat rectangular surface with collision and
    visual geometry.
  \item[\file{meshes/}]
    \texttt{.dae} or \texttt{.stl} mesh assets referenced by the SDF.
  \item[\file{materials/}]
    Ogre material scripts for the table surface texture.
\end{description}

Referenced by \file{ur3e\_on\_table.sdf} as a \texttt{<include>} directive.

\newpage
% ═══════════════════════════════════════════════════════════════
\section{Upstream / Third-Party Packages}
% ═══════════════════════════════════════════════════════════════

These packages are not original code but are vendored in \file{src/}
because either a specific (patched) version is required, or the package
is not available as an \texttt{apt} binary for this ROS\,2 Humble
installation.

% ───────────────────────────────────────────────────────────────
\subsection{\texttt{Universal\_Robots\_ROS2\_Driver} --- UR robot driver}
% ───────────────────────────────────────────────────────────────

The official Universal Robots ROS\,2 driver. Contains seven sub-packages:

\begin{center}
\begin{tabular}{|l|p{9cm}|}
\hline
\textbf{Sub-package} & \textbf{Role} \\
\hline
\pkg{ur\_robot\_driver} &
  Main driver node. Opens a TCP connection to the UR controller,
  streams joint states at 500\,Hz, and executes trajectories sent by
  MoveIt\,2 via the \texttt{scaled\_joint\_trajectory\_controller}. \\
\hline
\pkg{ur\_bringup} &
  Top-level launch files for the real robot
  (\file{ur\_control.launch.py}, \file{ur\_moveit.launch.py}). \\
\hline
\pkg{ur\_calibration} &
  Reads the robot-specific DH parameter correction from the UR controller
  and saves it as \file{my\_ur3e\_calibration.yaml}. \\
\hline
\pkg{ur\_controllers} &
  Custom ROS\,2 controllers: speed scaling, GPIO, force-torque, etc. \\
\hline
\pkg{ur\_moveit\_config} &
  MoveIt\,2 configuration shipped with the driver (used by
  \file{ur\_bringup/ur\_moveit.launch.py}). \\
\hline
\pkg{ur\_dashboard\_msgs} &
  Custom message and service definitions for the UR Dashboard server
  (power on/off, program load, etc.). \\
\hline
\pkg{ur} &
  Meta-package that declares the dependency tree for the whole driver. \\
\hline
\end{tabular}
\end{center}

% ───────────────────────────────────────────────────────────────
\subsection{\texttt{Universal\_Robots\_ROS2\_Description} --- Robot URDF and meshes}
% ───────────────────────────────────────────────────────────────

Visual and collision meshes (\texttt{.dae}/\texttt{.stl}) plus Xacro macros
for all UR robot models (UR3e, UR5e, UR10e, \ldots). This package is the
single source of truth for the UR3e kinematics and geometry; both
\pkg{ur\_moveit} and \pkg{ur\_sim} reference it via
\texttt{\$(find ur\_description)}.

This is the largest package by disk size ($\approx 70$\,MB) because it
bundles high-resolution collision and visual meshes for every UR model.

% ───────────────────────────────────────────────────────────────
\subsection{\texttt{Universal\_Robots\_ROS2\_GZ\_Simulation} --- Gazebo simulation}
% ───────────────────────────────────────────────────────────────

Contains the single sub-package \pkg{ur\_simulation\_gz}. Provides Gazebo
Ignition launch files and SDF world configurations designed to work with
the UR driver stack. \pkg{ur\_sim} extends and replaces the worlds from this
package with project-specific ones (\file{ur3e\_on\_table.sdf}, etc.).

% ───────────────────────────────────────────────────────────────
\subsection{\texttt{ros2\_control} --- ROS\,2 control framework}
% ───────────────────────────────────────────────────────────────

The core real-time control framework. Vendored here to pin a specific
version. Contains ten sub-packages:

\begin{center}
\begin{tabular}{|l|p{9cm}|}
\hline
\textbf{Sub-package} & \textbf{Role} \\
\hline
\pkg{hardware\_interface} & Base classes for hardware plugins (actuator, sensor, system). \\
\hline
\pkg{controller\_interface} & Base class for all ROS\,2 controllers. \\
\hline
\pkg{controller\_manager} & Loads, starts, stops, and switches controllers at runtime. \\
\hline
\pkg{controller\_manager\_msgs} & Service/action definitions for the controller manager. \\
\hline
\pkg{joint\_limits} / \pkg{joint\_limits\_interface} &
  Enforce joint position, velocity, and effort limits. \\
\hline
\pkg{transmission\_interface} & Maps actuator space to joint space (gear ratios, etc.). \\
\hline
\pkg{ros2controlcli} & Command-line tools (\texttt{ros2 control list\_controllers}, etc.). \\
\hline
\pkg{rqt\_controller\_manager} & rqt GUI plugin for managing controllers. \\
\hline
\pkg{ros2\_control\_test\_assets} & Shared URDF and config fixtures for unit tests. \\
\hline
\pkg{hardware\_interface\_testing} & Test helpers for hardware interface implementations. \\
\hline
\end{tabular}
\end{center}

% ───────────────────────────────────────────────────────────────
\subsection{\texttt{gz\_ros2\_control} --- Gazebo Ignition hardware interface}
% ───────────────────────────────────────────────────────────────

Bridges \pkg{ros2\_control} with Gazebo Ignition/Fortress. Contains:

\begin{center}
\begin{tabular}{|l|p{9cm}|}
\hline
\textbf{Sub-package} & \textbf{Role} \\
\hline
\pkg{gz\_ros2\_control} &
  The \texttt{IgnitionSystem} hardware plugin. Reads joint positions from
  the Gazebo physics simulation and applies torque commands from controllers. \\
\hline
\pkg{ign\_ros2\_control} & Compatibility shim for the older Ignition package name. \\
\hline
\pkg{gz\_ros2\_control\_demos} & Example robots demonstrating the plugin. \\
\hline
\pkg{ign\_ros2\_control\_demos} & Same demos under the legacy name. \\
\hline
\pkg{gz\_ros2\_control\_tests} & Integration tests. \\
\hline
\end{tabular}
\end{center}

% ───────────────────────────────────────────────────────────────
\subsection{\texttt{aruco\_ros} --- ArUco marker detection}
% ───────────────────────────────────────────────────────────────

ROS\,2 wrapper around the \texttt{aruco} C++ library. Used during
hand-eye calibration to detect the ArUco marker fixed in the scene.

\begin{center}
\begin{tabular}{|l|p{9cm}|}
\hline
\textbf{Sub-package} & \textbf{Role} \\
\hline
\pkg{aruco} &
  Standalone C++ library implementing ArUco marker detection and pose
  estimation (no ROS dependency). Compiles to \texttt{libaruco.so}. \\
\hline
\pkg{aruco\_msgs} &
  Custom message definitions: \texttt{Marker.msg} (ID, pose, confidence)
  and \texttt{MarkerArray.msg}. \\
\hline
\pkg{aruco\_ros} &
  ROS\,2 node (\texttt{aruco\_ros single}) that subscribes to an image
  topic and camera info, detects one or multiple ArUco markers, and
  publishes their poses as TF transforms and \texttt{Marker} messages. \\
\hline
\end{tabular}
\end{center}

During calibration the node is run as:
\begin{verbatim}
ros2 run aruco_ros single --ros-args \
  -p marker_size:=0.100 -p marker_id:=582 \
  -p camera_frame:=camera_color_optical_frame \
  -p marker_frame:=aruco_marker_frame \
  -r /image:=/camera/camera/color/image_raw
\end{verbatim}

% ───────────────────────────────────────────────────────────────
\subsection{\texttt{easy\_handeye2} --- Hand-eye calibration}
% ───────────────────────────────────────────────────────────────

Implements eye-in-hand hand-eye calibration (Tsai-Lenz or ANDREFF algorithm).
Records robot end-effector poses and corresponding marker poses as the robot
moves to different configurations, then solves for the camera-to-tool transform.

\begin{center}
\begin{tabular}{|l|p{9cm}|}
\hline
\textbf{Sub-package} & \textbf{Role} \\
\hline
\pkg{easy\_handeye2} &
  Calibration server node, RViz and rqt GUIs, and \file{calibrate.launch.py}.
  The result is saved to \file{ur3e\_d435.calib} at the workspace root. \\
\hline
\pkg{easy\_handeye2\_msgs} &
  Custom service and message types used by the calibration protocol. \\
\hline
\end{tabular}
\end{center}

% ───────────────────────────────────────────────────────────────
\subsection{\texttt{ros2\_robotiq\_gripper} --- Robotiq 2F-85 driver}
% ───────────────────────────────────────────────────────────────

ROS\,2 driver and description for the Robotiq 2F-85 adaptive gripper.

\begin{center}
\begin{tabular}{|l|p{9cm}|}
\hline
\textbf{Sub-package} & \textbf{Role} \\
\hline
\pkg{robotiq\_description} &
  URDF/Xacro macros and meshes for the 2F-85 gripper, used in the
  Robotiq-based robot description in \pkg{ur\_sim}. \\
\hline
\pkg{robotiq\_controllers} &
  ROS\,2 controller that sends gripper open/close commands over the
  Modbus RTU or Ethernet interface to the physical gripper. \\
\hline
\end{tabular}
\end{center}

% ───────────────────────────────────────────────────────────────
\subsection{\texttt{onrobot\_2FG7\_gripper\_description} --- OnRobot 2FG7 description}
% ───────────────────────────────────────────────────────────────

URDF/Xacro macros and meshes for the OnRobot 2FG7 two-finger gripper.
Referenced by \file{ur\_sim/urdf/ur3e\_gripper.urdf.xacro} and loaded by
\pkg{ur\_gripper\_moveit}.

\begin{itemize}
  \item \file{urdf/onrobot\_2fg7.xacro} --- kinematic macro with finger links and joints.
  \item \file{meshes/} --- \texttt{.stl} collision and visual meshes.
  \item \file{config/} --- joint limit parameters.
  \item \file{launch/} --- standalone view launch file.
\end{itemize}

% ───────────────────────────────────────────────────────────────
\subsection{\texttt{pymoveit2} --- Python MoveIt\,2 API}
% ───────────────────────────────────────────────────────────────

A pure-Python wrapper around the MoveIt\,2 ROS\,2 action and service
interfaces. Exposes a simple \texttt{MoveIt2} class used by all motion
scripts:

\begin{verbatim}
arm = MoveIt2(node, joint_names, base_link_name,
              end_effector_name, group_name)
arm.move_to_pose(pose)              # Cartesian goal
arm.move_to_configuration(joints)  # Joint-space goal
arm.wait_until_executed()
\end{verbatim}

Vendored in \file{src/} because the PyPI release lags behind the upstream
repository and some API methods used here (e.g.\ \texttt{cartesian=True}
keyword argument) require a specific commit.

% ───────────────────────────────────────────────────────────────
\subsection{\texttt{my\_robot\_calibration.yaml} (inside src/)}
% ───────────────────────────────────────────────────────────────

An earlier version of the UR3e kinematic calibration file stored inside
\file{src/} instead of the workspace root. It appears to be a predecessor
of \file{../my\_ur3e\_calibration.yaml} (the one referenced in the
\file{commandes\_detection\_and\_p\&p} launch commands). Verify that both
files contain the same calibration data before deleting this one.

\newpage
% ═══════════════════════════════════════════════════════════════
\section{Summary Table}
% ═══════════════════════════════════════════════════════════════

\begin{longtable}{|p{5cm}|p{2.5cm}|p{7cm}|}
\hline
\textbf{File / Package} & \textbf{Type} & \textbf{Role} \\
\hline
\endfirsthead
\hline
\textbf{File / Package} & \textbf{Type} & \textbf{Role} \\
\hline
\endhead
\hline
\endfoot
\hline
\endlastfoot

\pkg{shoe\_detector/yolo\_node.py} & Python node & 2-D YOLO detector, publishes bounding boxes \\
\hline
\pkg{shoe\_detector/grasp\_detector.py} & Python node & YOLO + PCA + depth $\to$ 3-D grasp point in \texttt{base\_link} \\
\hline
\file{shoe\_detector/config/handeye.yaml} & Config & Stored hand-eye calibration transform \\
\hline
\file{shoe\_detector/launch/perception.launch.py} & Launch & Starts camera + hand-eye TF for real-robot operation \\
\hline
\file{shoe\_detector/models/best\_kaagle\_10mars.pt} & ML weights & Trained YOLO segmentation model \\
\hline
\file{ur\_sim/urdf/ur3e.urdf.xacro} & URDF & UR3e (no gripper) top-level description \\
\hline
\file{ur\_sim/urdf/ur3e\_gripper.urdf.xacro} & URDF & UR3e + OnRobot 2FG7 top-level description \\
\hline
\file{ur\_sim/urdf/robotiq\_2f\_85\_*.xacro} & URDF & Robotiq 2F-85 macro and description \\
\hline
\file{ur\_sim/urdf/*.ros2\_control.xacro} & URDF & Hardware interface declarations \\
\hline
\file{ur\_sim/worlds/*.sdf} & World & Gazebo Ignition simulation worlds \\
\hline
\file{ur\_sim/config/*.yaml} & Config & Controller manager and initial pose config \\
\hline
\file{ur\_sim/launch/spawn\_*.launch.py} & Launch & Spawn robot in Gazebo (with/without MoveIt\,2) \\
\hline
\file{ur\_sim/launch/view\_*.launch.py} & Launch & Visualise URDF in RViz only \\
\hline
\file{ur\_sim/scripts/pick\_and\_place\_grasp.py} & Script & \textbf{Production:} detector-driven pick-and-place \\
\hline
\file{ur\_sim/scripts/pick\_and\_place.py} & Script & Fixed-coordinate pick-and-place (reference) \\
\hline
\file{ur\_sim/scripts/stack.py} & Script & Cube-stacking demo with TF\,2 arrival verification \\
\hline
\file{ur\_sim/scripts/tp\_ar.py} & Script & Joint-angle validation / IK lab tool \\
\hline
\file{ur\_sim/scripts/grasp\_test.py} & Dev script & Earlier grasp-driven pick-and-place prototype \\
\hline
\file{ur\_sim/scripts/pick\_place\_test.py} & Dev script & Intermediate pick-and-place prototype \\
\hline
\file{ur\_sim/scripts/pick\_test.py} & Dev script & Pick-only motion test \\
\hline
\file{ur\_sim/scripts/stack\_old.py} & Dev script & Superseded stacking script \\
\hline
\file{ur\_sim/scripts/stack (copy).py} & Dev script & Copy of stack.py; safe to delete \\
\hline
\file{ur\_sim/scripts/stack\_bu\_new.py} & Dev script & Backup of stack.py; safe to delete \\
\hline
\file{ur\_sim/scripts/sb.py}, \file{sb2.py} & Dev script & Sandbox snippets; safe to delete \\
\hline
\file{ur\_sim/scripts/test.py}, \file{test\_move.py} & Dev script & Early movement tests; safe to delete \\
\hline
\pkg{ur\_moveit} (all files) & MoveIt\,2 pkg & MoveIt\,2 config for bare UR3e \\
\hline
\pkg{ur\_gripper\_moveit} (all files) & MoveIt\,2 pkg & MoveIt\,2 config for UR3e + OnRobot 2FG7 \\
\hline
\pkg{Universal\_Robots\_ROS2\_Driver} & Upstream & Real robot TCP driver + controllers \\
\hline
\pkg{Universal\_Robots\_ROS2\_Description} & Upstream & UR3e URDF + meshes (source of truth) \\
\hline
\pkg{Universal\_Robots\_ROS2\_GZ\_Simulation} & Upstream & Gazebo base worlds for UR \\
\hline
\pkg{ros2\_control} & Upstream & Real-time controller framework \\
\hline
\pkg{gz\_ros2\_control} & Upstream & Gazebo Ignition hardware plugin \\
\hline
\pkg{aruco\_ros} & Upstream & ArUco marker detection (calibration) \\
\hline
\pkg{easy\_handeye2} & Upstream & Hand-eye calibration workflow \\
\hline
\pkg{ros2\_robotiq\_gripper} & Upstream & Robotiq 2F-85 driver + description \\
\hline
\pkg{onrobot\_2FG7\_gripper\_description} & Upstream & OnRobot 2FG7 URDF + meshes \\
\hline
\pkg{pymoveit2} & Upstream & Python MoveIt\,2 API \\
\hline
\pkg{models/class\_table} & Asset & Gazebo table SDF model \\
\hline
\file{my\_robot\_calibration.yaml} & Data & Earlier robot kinematics calibration (verify vs.\ root copy) \\
\hline
\end{longtable}

\end{document}
